---
title: "Day 7 Practice"
output: html_document
---

In this practice, let's explore data on tipping, in the `tips` data frame from the `reshape2` package.

0. First get a little familiar with the structure of the data, using `summary()`, `head()`, etc.  What are the numeric variables?  What are their units? What about factors? Are factor levels sensible?

```{r}

#install.packages("scales")

library(scales)
library(reshape2)
library(ggplot2)
library(graphics)

summary(tips)
head(tips)

#Sex, Smoker, Day, Time appear to be Factors
#Total Bill, Tip, Size appear to be Numeric

```

1. Create a simple scatterplot, plotting the tip amount by the total bill.
  - first plot the raw quantities
  - "save" the initial simple plot as an object
  - change the axis labels for both x and y
    - try two different methods
  
```{r}
mytips <- tips

#Total_Bill x Sex x Time
ggplot(data = mytips, aes(total_bill))+geom_histogram()
ggplot(mytips, aes(total_bill)) + geom_histogram(aes(fill = time)) + facet_wrap(~sex) + xlab("dollars spent")+ylab("Frequency")

mytips$tip

#Tips x Sex x Time
ggplot(data = mytips, aes(tip))+geom_histogram()
ggplot(mytips, aes(tip)) + geom_histogram(aes(fill = time)) + facet_wrap(~sex) + xlab("dollars spent")+ylab("Frequency")


#Boxplots
ggplot(data = mytips, aes(sex, total_bill))+geom_boxplot()
ggplot(data = mytips, aes(sex, tip))+geom_boxplot()


#ggplot(scottdata, aes(Corpus, log(WithinMinPairs + .2))) + geom_boxplot()

```
```{r}

seahawks <- scale_color_manual(values = c("darkblue", "green", "steel"))

ggplot(data = mytips, aes(x = total_bill, y = tip, color = sex)) + 
  geom_point(size = 4) + 
  theme_minimal() +
  geom_smooth(method = "lm") +
  seahawks


```
2. Continue using the previous data
  - using `scales`, plot the axes so that they follow a logarithmic pattern
  - add "break" values every 5 dollars on the x axis, and every 2 dollars on the y axis
  - finally, use `labels = dollar` (made available by the `scales` package) to format the axis numbers as dollars

```{r}
bill.tip.scatter <- ggplot(data = mytips, aes(x = total_bill, y = tip, color = sex)) + 
  geom_point(size = 4) + 
  theme_minimal() +
  geom_smooth(method = "lm") +
  seahawks

#same data now just scattered
bill.tip.scatter + scale_x_log10(labels = c("$0", "$5", "$10","$15","$20","$25","$30","$35","$40","$45", "$50"), breaks = seq(0,50,5))+scale_y_log10(labels = c("$0","$2", "$4","$6","$8","$10"), breaks = seq(0,10,2))


#same data, scattered and name of labels
bill.tip.scatter + scale_x_log10(labels = dollar, breaks = seq(0,50,5), name = "Total Bill")+scale_y_log10(labels = c("$0","$2", "$4","$6","$8","$10"), breaks = seq(0,10,2), name = "Tip")


#same data, plus information on smoking
bill.tip.scatter + scale_x_log10(labels = dollar, breaks = seq(0,50,5), name = "Total Bill")+scale_y_log10(labels = c("$0","$2", "$4","$6","$8","$10"), breaks = seq(0,10,2), name = "Tip")

ggplot(data = mytips, aes(x = total_bill, y = tip, color = sex, shape = smoker)) + 
  geom_point(size = 4) + 
  theme_minimal() +
  geom_smooth(method = "lm") +
  seahawks + scale_x_log10(labels = dollar, breaks = seq(0,50,5), name = "Total Bill")+scale_y_log10(labels = c("$0","$2", "$4","$6","$8","$10"), breaks = seq(0,10,2), name = "Tip")



#same, data, now change the font for everything
ggplot(data = mytips, aes(x = total_bill, y = tip, color = sex, shape = smoker)) + 
  geom_point(size = 4) + 
  theme_minimal() +
  geom_smooth(method = "lm") +
  seahawks + scale_x_log10(labels = dollar, breaks = seq(0,50,5), name = "Total Bill")+scale_y_log10(labels = c("$0","$2", "$4","$6","$8","$10"), breaks = seq(0,10,2), name = "Tip") + theme(text = element_text(family = "serif", size = 15))
          #element_text changes all

#same, data, now add a title
ggplot(data = mytips, aes(x = total_bill, y = tip, color = sex, shape = smoker)) + 
  geom_point(size = 4) + 
  theme_minimal() +
  geom_smooth(method = "lm") +
  seahawks + scale_x_log10(labels = dollar, breaks = seq(0,50,5), name = "Total Bill")+scale_y_log10(labels = c("$0","$2", "$4","$6","$8","$10"), breaks = seq(0,10,2), name = "Tip") + theme(text = element_text(family = "serif", size = 15))+ggtitle("Awesome")
    #(0,50,5)   #minimum, maximum, by what number

#now with facet wrap & information on days
ggplot(data = mytips, aes(x = total_bill, y = tip, color = sex, shape = smoker)) + 
  geom_point(size = 4) + 
  theme_minimal() +
  geom_smooth(method = "lm") +
  seahawks + scale_x_log10(labels = dollar, breaks = seq(0,50,5), name = "Total Bill")+scale_y_log10(labels = c("$0","$2", "$4","$6","$8","$10"), breaks = seq(0,10,2), name = "Tip") + theme(text = element_text(family = "serif", size = 12))+ggtitle("Awesome")+facet_wrap(~day)


```
```{r}
####Names for Fantasy

geom_text(aes(color = sex, label = player))
```

3. Continue to build off of the final scatterplot in the previous problem (hint: you may need to change the plot object, in order to make the following changes)
  - map gender to the color of the points
  - change the color values, using both the "brewer" and "manual" methods
  - add regression lines (regular linear regression), which also break down by gender
  - also try a loess smoother instead of regression lines
  - finally, change the overall "theme" to either the "classic", "minimal", or "bw" theme

```{r}
bill.tip.scatter + scale_x_log10(labels = c("$0", "$5", "$10","$15","$20","$25","$30","$35","$40","$45", "$50"), breaks = seq(0,50,5))+scale_y_log10(labels = c("$0","$2", "$4","$6","$8","$10"), breaks = seq(0,10,2))+theme_minimal()

```


4. Now let's modify the legend for the `sex` variable, building off off the scatterplot with linear regression lines
  - using the appropriate `scale` function, change the name of the legend to "Gender"
  - change the location of the legend with the `theme()` function
  - also using the "legend.position" argument, remove the legend completely
  - finally, put the legend back to the default position, but change the levels, such that Male is given as the first level
  
```{r}

```

5. Let's explore how this pattern might vary for different days of the week.
  - use faceting to create a separate plot for each day
  - try both the "wrap" and "grid" faceting functions
  - make a change so that the labels on the top of the facets give the full day name (e.g., "Friday", not "Fri"), and they are ordered from Thursday to Sunday
  
```{r}


```

6. Now let's look at adding information about the size of the party to the plot
  - first leave off the regression lines, to make it easier to see
  - map party size to the size of the points
  - look at both an aggregate plot and plots faceted by day
  - now add back the regression lines, but only plot a single regression line (i.e., not broken down by gender), remove the confidence interval (hint: look at the arguments for `geom_smooth()`), and make the line a dashed black line
  
```{r}

```

