---
title: "Day 7 Homework"
output: html_document
---
Jordan Epistola

```{r}
library(readxl)
library(BayesFactor)
library(ggplot2)
library(tidyr)
library(dplyr)
```

```{r}
FantasyFootball2014 <- read_xlsx("../Datasets/Fantasy Football 2014.xlsx", skip = 2)
FantasyFootball2015 <- read_xlsx("../Datasets/Fantasy Football 2015.xlsx", skip = 2)

head(FantasyFootball2014)
```


Find three relationships in your data.  For each relationship, do the following:

1. Verbally articulate the relationship you want to examine with a plot.

#1) Distribution of 2014 & 2015 PPR points per Game by Position. Identify Outliers if Possible.
#2) Relationship of Receptions, Targets & Fantasy PPR Points
#3)  

2. Verbally identify what variables you want to map to each graphical dimension.

3. Reshape your data as needed.

```{r}
#1) Distribution of 2014 & 2015 PPR points per Game by Position. Label Outliers.
A1.Players <- c(FantasyFootball2014$Player, FantasyFootball2015$Player)
A1.Positions <- c(FantasyFootball2014$Pos, FantasyFootball2015$Pos)
A1.Year <- c(rep("2014", 141), rep("2015", 141))
A1.PPG.2014.2015 <- c(FantasyFootball2014$PPR__1, FantasyFootball2015$PPR__1)

AnalysisOne.Data <- cbind.data.frame(A1.Players, A1.Positions, A1.Year, A1.PPG.2014.2015)
#View(AnalysisOne.Data)


#2) Relationship between 2014 PPR Points & 2015 PPR Points per Game based on Position.
A2.Players <- FantasyFootball2014$Player
A2.Position <- FantasyFootball2014$Pos
A2.Probowl <- as.factor(FantasyFootball2014$PB)

levels(A2.Probowl) <- c("No Pro-Bowl", "Pro-Bowl")
#levels(A2.Probowl)

A2.PPG.2014 <- FantasyFootball2014$PPR__1
A2.PPG.2015 <- FantasyFootball2015$PPR__1

AnalysisTwo.Data <- cbind.data.frame(A2.Players,A2.Position,A2.Probowl, A2.PPG.2014,A2.PPG.2015)


#3) Relationship between 2015 PPR Points, Completion Percentage, QB Ranking (2014) by Position
A3.Players <- (FantasyFootball2014$Player)
A3.Position <- (FantasyFootball2014$Pos)
A3.Win <- FantasyFootball2014$`# Win`
A3.QB.Com <- (FantasyFootball2014$Per)
A3.QB.Rank <- FantasyFootball2014$Rate
A3.PPG.2014 <- FantasyFootball2014$PPR__1
A3.PPG.2015 <- FantasyFootball2015$PPR__1

AnalysisThree.Data <- cbind.data.frame(A3.Players, A3.Position, A3.Win, A3.QB.Com, A3.QB.Rank, A3.PPG.2014, A3.PPG.2015)

```

4. Use ggplot2 to create your graphs.

```{r}
#1) Distribution of 2014 & 2015 PPR points per Game by Position.
Plot1 <- ggplot(data = AnalysisOne.Data, aes(A1.Positions, A1.PPG.2014.2015))+geom_boxplot()+facet_wrap(~A1.Year)+ggtitle("Fantasy Points per Game by Position")+xlab("Position")+ylab("2015 Fantasy Points per Game (PPR)")


#2) Relationship between 2014 PPR Points & 2015 PPR Points per Game based on Position.    
Plot2 <- ggplot(data = AnalysisTwo.Data, aes(x = log(A2.PPG.2014), y = log(A2.PPG.2015), color = A2.Position))+geom_point()+geom_smooth(method = "lm", se = FALSE)+facet_wrap(~A2.Probowl)+xlab("Points per Game 2014 (PPR)")+ylab("Points per Game 2015 (PPR)")


#3) Relationship between PPR Points & QB Ranking by Position for 2014 & 2015
Plot3 <- ggplot(data = AnalysisThree.Data, aes(x = A3.QB.Com, y = A3.PPG.2015, size = A3.QB.Rank, color = A3.Win))+geom_point()+facet_wrap(~A3.Position)

```

5. Fiddle with colors, axis labels, themes, etc. until the plot looks "publication ready" to you.  Try to change at least one thing per plot.

```{r}
#1) Distribution of 2014 & 2015 PPR points per Game by Position

      #Outlier Labels
      is_outlier <- function(x) {
      return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))}

AnalysisOne.Data %>%
  group_by(A1.Positions) %>%
  mutate(outlier = ifelse(is_outlier(A1.PPG.2014.2015), A1.PPG.2014.2015, as.numeric(NA))) %>% 
           ggplot(., aes(x = factor(A1.Positions), y = A1.PPG.2014.2015))+geom_boxplot()+facet_wrap(~A1.Year)+ ggtitle("Fantasy Points per Game by Position for 2014 & 2015 Seasons")+xlab("Position")+ylab("2015 Fantasy Points per Game (PPR)")+geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3)

                #This code is supposed to label the outliers... Why is this not working?


###### Class Note ######

#How to Label Outliers, Need to add New Geom Layer of Text

ggplot(AnalysisOne.Data , aes(x = factor(A1.Positions), y = A1.PPG.2014.2015))+geom_boxplot()+facet_wrap(~A1.Year)+ ggtitle("Fantasy Points per Game by Position for 2014 & 2015 Seasons")+xlab("Position")+ylab("2015 Fantasy Points per Game (PPR)")+geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3) + geom_text(A, aes(x = ))


A <- (AnalysisOne.Data$A1.Players[AnalysisOne.Data$A1.PPG.2014.2015 > 18 & AnalysisOne.Data$A1.Positions == "WR" & AnalysisOne.Data$A1.Year == "2014"])
A <- as.data.frame(A)


```     


```{r}
#2) Relationship between 2014 PPR Points & 2015 PPR Points per Game based on Position.    

seahawks <- scale_color_manual(values = c("darkblue", "green", "grey"))

ggplot(data = AnalysisTwo.Data, aes(x = log(A2.PPG.2014), y = log(A2.PPG.2015), color = A2.Position))+geom_point()+geom_smooth(method = "lm", se = FALSE)+facet_wrap(~A2.Probowl)+xlab("Points per Game 2014 (PPR)")+ylab("Points per Game 2015 (PPR)")+ seahawks + ggtitle("2014 Fantasy Points per Game by 2015 Fantasy Points per Game") + labs(col = "Position")

Bayes.A2 <- generalTestBF(A2.PPG.2015 ~ A2.Probowl + A2.PPG.2014, data = AnalysisTwo.Data)
Bayes.A2
#No Significant Relationship between 2014 PPG(PPR) & 2015 PPG(PPR)
```

```{r}
#3) Relationship between PPR Points & QB Ranking by Position for 2014 & 2015

ggplot(data = AnalysisThree.Data, aes(x = A3.Win, y = A3.PPG.2015, size = A3.QB.Rank, color = A3.QB.Com))+geom_point()+facet_wrap(~A3.Position)+xlab("Number of Team Wins")+ylab("2015 Fantasy Points per Game(PPR)")+ggtitle("2015 Points per Game by 2014 QB Rate, QB Percent & # of Wins") + labs(col = "QB Completion Percent", size = "QB Rating")


Bayes.A3 <- generalTestBF(A3.PPG.2015 ~ A3.QB.Com + A3.QB.Rank + A3.Win, data = AnalysisThree.Data)
Bayes.A3

max(Bayes.A3)


```


6. Save all plots to a format that you could use in a paper.  HINT: PNG works well for pasting into Word documents.

```{r}

png("day7HW.png", width = 600, height = 800)

#Question 1
      #Outlier Labels
      is_outlier <- function(x) {
      return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))}

AnalysisOne.Data %>%
  group_by(A1.Positions) %>%
  mutate(outlier = ifelse(is_outlier(A1.PPG.2014.2015), A1.PPG.2014.2015, as.numeric(NA))) %>% 
           ggplot(., aes(x = factor(A1.Positions), y = A1.PPG.2014.2015))+geom_boxplot()+facet_wrap(~A1.Year)+ ggtitle("Fantasy Points per Game by Position for 2014 & 2015 Seasons")+xlab("Position")+ylab("2015 Fantasy Points per Game (PPR)")+geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3)

png("day7HW2.png", width = 600, height = 800)

#Question 2
ggplot(data = AnalysisTwo.Data, aes(x = log(A2.PPG.2014), y = log(A2.PPG.2015), color = A2.Position))+geom_point()+geom_smooth(method = "lm")+facet_wrap(~A2.Probowl)+xlab("Points per Game 2014 (PPR)")+ylab("Points per Game 2015 (PPR)")+ seahawks + ggtitle("2014 Fantasy Points per Game by 2015 Fantasy Points per Game") + labs(col = "Position")

png("day7HW3.png", width = 600, height = 800)

#Question 3
ggplot(data = AnalysisThree.Data, aes(x = A3.Win, y = A3.PPG.2015, size = A3.QB.Rank, color = A3.QB.Com))+geom_point()+facet_wrap(~A3.Position)+xlab("2014 QB Competion Rate")+ylab("2015 Fantasy Points per Game(PPR)")+ggtitle("2015 Points per Game by QB Rate, QB Percent & # of Team Wins") + labs(col = "QB Completion Percent", size = "QB Rating")


dev.off()

```

