---
title: "Day 5 Homework"
output: html_document
---

0. Reload your data, and re-use the code you already have for getting things formatted nicely (columns renamed, factors relabeled, etc.)

```{r}
<<<<<<< HEAD
library(readxl)

FantasyFootball2014 <- read_excel("../../my_r_homework/Datasets/Fantasy Football 2014.xlsx", skip = 2)
FantasyFootball2015 <- read_excel("../../my_r_homework/Datasets/Fantasy Football 2015.xlsx", skip = 2)

head(FantasyFootball2014)
head(FantasyFootball2015)

#summary(FantasyFootball2014)
FantasyFootball2014$Pos <- as.factor(FantasyFootball2014$Pos)
FantasyFootball2014$Team <- as.factor(FantasyFootball2014$Team)

FantasyFootball2015$Pos <- as.factor(FantasyFootball2015$Pos)
FantasyFootball2015$Team <- as.factor(FantasyFootball2015$Team)
#summary(FantasyFootball2014)
#summary(FantasyFootball2015)
=======
library(tidyverse)
scottdata <- read.csv("scottdata/CognitionPaperFinalData.csv")
>>>>>>> e767846704d25eb9c9bdbaacee4b502ea4ff5284
```

1. Aggregate (e.g., get mean/median/max/something) of some numerical variable, over one or more factors.  Use `group_by()` plus `summarize()` from the `dplyr` package. You may or may not need to reshape the data first!

```{r}
<<<<<<< HEAD
library(dplyr)
=======
# normal "nested" syntax
summarize(group_by(scottdata, Merged), 
          meanMP = mean(BetweenMinPairs), 
          medianMP = median(BetweenMinPairs), 
          sdMP = sd(BetweenMinPairs), 
          N = length(BetweenMinPairs), 
          seMP = sd(BetweenMinPairs)/sqrt(length(BetweenMinPairs)))

# "piped" syntax
group_by(scottdata, Merged) %>% summarize(meanMP = mean(BetweenMinPairs), 
                                          medianMP = median(BetweenMinPairs), 
                                          sdMP = sd(BetweenMinPairs), 
                                          N = length(BetweenMinPairs), 
                                          seMP = sd(BetweenMinPairs)/sqrt(length(BetweenMinPairs)))
>>>>>>> e767846704d25eb9c9bdbaacee4b502ea4ff5284

#Create Position Analysis Dataframe
#FantasyFootball2014x2015 <- merge(FantasyFootball2014, FantasyFootball2015, by = "Player")
FantasyFootball2014x2015 <- cbind(FantasyFootball2014, FantasyFootball2015)
    #View(FantasyFootball2014x2015)


Position.Analysis <- data.frame(FantasyFootball2014x2015$Player, FantasyFootball2014x2015$Pos, FantasyFootball2014x2015$DP, FantasyFootball2014x2015$`1st`, FantasyFootball2014x2015$Yds, FantasyFootball2014x2015$TD, FantasyFootball2014x2015$`1st__1`,FantasyFootball2014x2015$Yds__1, FantasyFootball2014x2015$TD__1, FantasyFootball2014$PPG, FantasyFootball2015$PPG)

names(Position.Analysis) <- c("Player", "Position", "Downs Played", "1st Downs Rushing", "Yards Rushing", "Touchdowns Rushing", "1st Downs Recieving", "Yards Recieving", "Touchdowns Recieving", "2014 PPG", "2015 PPG")
#head(Position.Analysis)


#Aggregate Data
      #Total Number of First Downs by Position (2014) (Rushing + Recieving)
      #Total Number of Yards by Position (2014) (Rushing + Recieving)
      #Total Number of Touchdowns by Position (2014) (Rushing + Recieving)

Position.Analysis$Total.First.Downs <- (Position.Analysis$`1st Downs Rushing` + Position.Analysis$`1st Downs Recieving`)
Position.Analysis$Total.Yards <- (Position.Analysis$`Yards Rushing` + Position.Analysis$`Yards Recieving`)
Position.Analysis$Total.Touchdowns <- (Position.Analysis$`Touchdowns Rushing` + Position.Analysis$`Touchdowns Recieving`)

      #Median Number of total First downs by Position (2014)
      #Median Number of Yards by Position (2014)
      #Median Number of touchdowns by Position (2014)

Position.Analysis$Median.1st <- summarize(group_by(Position.Analysis, Player, Position), median = median(Total.First.Downs))
Position.Analysis$Median.Yrds <-
Position.Analysis$Median.Tds <-


```

<<<<<<< HEAD
2. Run TWO DIFFERENT simple analyses or statistical tests, such as linear regression (`lm()`), logistic regression (`glm()`), correlation test (`cor.test()`), t-test (`t.test()`), or non-parametric tests (e.g., `wilcox.test()`).  For each of these:
  - Describe why you are doing this analysis, i.e., what question is it answering?
  - I won't judge you on statistical expertise!  (though I will make comments if I think I can be helpful)
  - Report some key statistics from the analysis, using **inline** code. HINT: outside of an R code chunk, use `r codehere` format.
  
```{r}
<<<<<<< HEAD



=======
# Already there!
>>>>>>> e767846704d25eb9c9bdbaacee4b502ea4ff5284
```

3. Get your data into "long" (aka "tidy") format, if it isn't already
=======
2. Get your data into "long" (aka "tidy") format, if it isn't already
>>>>>>> 349832c192ab9e1da8ae37b589e9151f1f4a0781

```{r}

```


myff <- french_fries
head(myff)

# make long
myff.long <- gather(myff, flavor, rating, potato:painty)
head(myff.long)

# get "cell means"
ff.means <- summarize(group_by(myff.long, treatment, flavor), mean = mean(rating))
ff.means
ff.means <- summarize(group_by(myff.long, treatment, flavor), mean = mean(rating, na.rm = TRUE))
ff.means