---
title: "Day 5 Practice"
output: html_document
---

1. Make another copy of the iris data set
  - Using `data.frame()` create a (small) table that assigns a color to each species.  That is, make a column called Species and a column called Color, with one row per species
  - use `merge()` to merge the data into the copy of the iris data set
  - create another table with an additional species (and color)
  - merge this new table with iris. What happened?
  - create one more table matching species to color, with only two rows, missing setosa
  - merge this new table with the copy of iris. What happened?

```{r}
library(dplyr)
my.iris <- iris
species.color <- data.frame(Species = c("setosa", "virginica", "versicolor"),
                            Color = c("red", "blue", "yellow"))
species.color
iris.merge1 <- merge(my.iris, species.color) #, by = "Species")
head(iris.merge1)
nrow(iris.merge1)
xtabs(~ Species + Color, iris.merge1)

species.color2 <- data.frame(Species = c("setosa", "virginica", "versicolor", "scorpiris"),
                            Color = c("red", "blue", "yellow", "purple"))
species.color2
iris.merge2 <- merge(my.iris, species.color2, all = FALSE)
iris.merge3 <- merge(my.iris, species.color2, all = TRUE)
iris.merge4 <- left_join(my.iris, species.color2)
iris.merge4$Species <- as.factor(iris.merge4$Species)
nrow(my.iris)
nrow(iris.merge2)
nrow(iris.merge3)
nrow(iris.merge4)

species.color3 <- data.frame(Species = c("virginica", "versicolor"),
                            Color = c("blue", "yellow"))
species.color3
iris.merge5 <- merge(my.iris, species.color3, all = FALSE)
iris.merge6 <- merge(my.iris, species.color3, all = TRUE)
iris.merge7 <- left_join(my.iris, species.color3)
iris.merge7$Species <- as.factor(iris.merge7$Species)
nrow(my.iris)
nrow(iris.merge5)
nrow(iris.merge6)
nrow(iris.merge7)

#View(iris)
summary(iris$Species)


#This is how to do it correctly

#making small data frame
my.iris <- iris
species.color <- data.frame(Species = c("setosa", "virginica", "versicolor"), 
                            Color = c("red", "blue", "yellow"))

species.color
iris.merge1 <- merge(my.iris, species.color, by = "Species")
      # if it things this is a object, then put Quotes. If Quotes not found then try no quotes.

      # Checking Code
      head(iris.merge1)
      nrow(iris.merge1)
        xtabs(~ Species + Color, iris.merge1)
  
# New data Frame w/ color and new species
species.color2 <- data.frame(Species = c("setosa", "virginica", "versicolor", "scorpiris"), 
                            Color = c("red", "blue", "yellow", "purple"))
species.color2

iris.merge2 <- merge(my.iris, species.color2, by = "Species", all = FALSE) # all = False: End result only retain matching data
iris.merge3 <- merge(my.iris, species.color2, by = "Species", all = TRUE)  # all = TRUE: End result contains everything, including NAs

iris.merge4 <- left_join(my.iris, species.color2) # Keep data in old data set, but does not add everything (i.e. "scorpiris")
iris.merge4
      "Column `Species` joining factors with different levels, coercing to character vector --- we need to put Species back into Factor"
        iris.merge4$Species <- as.factor(iris.merge4$Species)
        
      # Checking Code
      head(iris.merge4)
      nrow(iris.merge2)
      nrow(iris.merge3)
      nrow(iris.merge4)
        xtabs(~ Species + Color, iris.merge1)
        

# New Data Frame w/ only virginica & versicolor color data | adding these data only
species.color3 <- data.frame(Species = c("virginica", "versicolor"), Color = c("blue", "yellow"))
species.color3

iris.merge5 <- merge(my.iris, species.color3, all = FALSE) #End result only retain matching data
iris.merge6 <- merge(my.iris, species.color3, all = TRUE)  #End result contains everything

iris.merge7 <- left_join(my.iris, species.color3)
iris.merge7


      # Checking Code
      head(iris.merge7)
      nrow(iris.merge5)
      nrow(iris.merge6)
      nrow(iris.merge7)
        xtabs(~ Species + Color, iris.merge7)
        

```


2. Make (yet another) copy of the iris data set
  - #Create a column that takes the log of the Sepal.Width
  - #Create a column that represents the multiplication of Sepal.Width by Sepal.Length
  - #Create a "median split" column on Sepal.Width. In other words, calculate the median of Sepal.Width, and then create a column that indicates whether the value in that row is less than the median or not
  
```{r}
my.iris <- iris
my.iris$log.Sepal.Width <- log(my.iris$Sepal.Width)
my.iris$Sepal.Area <- my.iris$Sepal.Width * my.iris$Sepal.Length

<<<<<<< HEAD
my.iris.copy <- iris

#Create a column that takes the log of the Sepal.Width
    my.iris.copy$log.sepal.width <- log(my.iris.copy$Sepal.Width)
    
#Create a column that represents the multiplication of Sepal.Width by Sepal.Length
    my.iris.copy$multiply.sw.sl <- ((my.iris.copy$Sepal.Width) * (my.iris.copy$Sepal.Length))
    
#Create a "median split" column on Sepal.Width. In other words, calculate the median of Sepal.Width, and then create a column that indicates whether the value in that row is less than the median or not
    median(my.iris.copy$multiply.sw.sl)
=======
median.Sepal.Width <- median(my.iris$Sepal.Width)

# one method
my.iris$median.split <- NA # not necessary (but maybe used to be?)
my.iris$median.split[my.iris$Sepal.Width < median.Sepal.Width]  <- "low"
my.iris$median.split[my.iris$Sepal.Width >= median.Sepal.Width] <- "high"

# another method
my.iris$median.split2 <- ifelse(test = my.iris$Sepal.Width < median.Sepal.Width, 
                               yes = "low", no = "high")
my.iris$median.split3 <- as.factor(ifelse(test = my.iris$Sepal.Width < median.Sepal.Width, 
                               yes = "low", no = "high"))


# another method
my.iris$median.split4 <- as.factor(my.iris$Sepal.Width < median.Sepal.Width)
levels(my.iris$median.split4) <- c("low", "high") # should be c("high", "low")

xtabs(~ Sepal.Width + median.split, my.iris)
xtabs(~ median.split + median.split2, my.iris)
xtabs(~ median.split + median.split3, my.iris)
xtabs(~ median.split + median.split4, my.iris)
>>>>>>> 349832c192ab9e1da8ae37b589e9151f1f4a0781

      median(my.iris.copy$Sepal.Width)
    my.iris.copy$median.greater.less <- (my.iris.copy$Sepal.Width > 3)
    my.iris.copy$median.greater.less
    
    #Another method (if-else)
    my.iris.copy$median.greater.less2 <- ifelse(test = my.iris.copy$Sepal.Width < median(my.iris.copy$Sepal.Width), yes = "low", no = "high")
    my.iris.copy$median.greater.less2
    
```

3. Start with (yes, you guessed it!) another copy of the iris data set
  - Use `gather()` to convert this wide data to long format
    - You should be "gathering up" all of the columns with measurements
  - "Tidy" up the new factor column by splitting it into two columns: one designating dimension (width vs. length), one designating flower part (sepal vs. petal)
    
```{r}
my.iris <- iris
my.iris$PlantID <- as.factor(paste("plant", 1:nrow(my.iris), sep = ""))
iris.long <- gather(my.iris, measurement, cm, Sepal.Length:Petal.Width)
head(iris.long)

<<<<<<< HEAD
my.iris3 <- iris

#conversion to long
=======
iris.long <- separate(iris.long, measurement, sep = "\\.", c("plant.part", "dimension"))
head(iris.long)
```
>>>>>>> 349832c192ab9e1da8ae37b589e9151f1f4a0781


<<<<<<< HEAD
iris.long <- gather(my.iris3, Variables, Values, Sepal.Length:Petal.Width)
head(iris.long)
    #lets make tracking ID
    my.iris$plantID <- (1:nrow(my.iris))
    #head(my.iris)
```
=======
```{r}
cell.means <- group_by(iris.long, plant.part, dimension, Species) %>% summarize(mean.cm = mean(cm))
head(cell.means)
cell.means.wide <- spread(cell.means, Species, mean.cm)
cell.means.wide
>>>>>>> 349832c192ab9e1da8ae37b589e9151f1f4a0781

**TIDY?????**
```{r}
#install.packages("lazyeval")
#library(tidyverse)
#tidy - still long but separate widths/length & flower parts

    iris.long1 <- separate(iris.long, Variables, sep = "\\.", c("plant.part", "dimension"))  
                          #splitting along the dots
    head(iris.long)
    head(iris.long1)
    
    
```

<<<<<<< HEAD
4. Continue working with the "long" iris data from previous problem
  - using `dplyr` functions, get the mean for each "cell" in the species x part x dimension design
  - make the results "wide", with different columns for each species

```{r}

```

  - use `summary()` to display the results.
  
```{r}

```

  - using INLINE code, report the estimate, standard error, and p-value for the WithinMinPairs coefficient.  Hint #1: save the summary as an object, and pull values from that. Hint #2: use `str()` to figure out how to extract these values. Hint #3: save the individual results as objects first, then put in inline code.

```{r}

```

The estimate is `r`, the standard error is `r`, and the p-value is `r`.

EXTRA CREDIT: figure out how to display the above results with only a few decimal places
=======
>>>>>>> 349832c192ab9e1da8ae37b589e9151f1f4a0781
