---
title: "Day 4 Homework"
output: html_document
---

1. Find some aspect of your data that needs to be combined or merged in some way.  This could be a variety of things:
  - multiple "sheets" in an Excel
  - multiple files that should be combined into one data set
  - properties that need to be merged in to one data set. For example:
    - you have a table of subject properties (gender, handedness, etc.) that need to be merged into the item-level data
    - you have other information on countries (population, etc.) that need to be merged in
  - if you DON'T have this naturally-occurring issue, figure out a way to manufacture it. For example:
    - split up your data into chunks
    - make up some new table of information that you want to merge in
  - Explain (in words) what you are trying to do
  - Use binding/merging commands to accomplish this
  - Complete at least ONE example of binding and ONE example of merging


This opens the Excel Sheets
```{r}
library(readxl) 

FantasyFootball2014 <- read_excel("../Datasets/Fantasy Football 2014.xlsx", skip = 2)
FantasyFootball2015 <- read_excel("../Datasets/Fantasy Football 2015.xlsx", skip = 2)

```

Lets try to combines these two Data sets into one
```{r}
# Combining these two Data sets into one

library(dplyr)

FantasyFootball_2014x2015 <- bind_cols(FantasyFootball2014, FantasyFootball2015)
View(FantasyFootball_2014x2015)



# Splitting Data into Two then Putting it Back Together

FantasyFootball_Left <- FantasyFootball_2014x2015[1:30]
FantasyFootball_Right <- FantasyFootball_2014x2015[31:59]

FantasyFootball_Combine <- cbind(FantasyFootball_Left, FantasyFootball_Right)
FantasyFootball_Combine


```

#Questions
    *How would you combine by columns if there is a differing number of rows*