---
title: "Day 4 Homework"
output: html_document
---

1. Find some aspect of your data that needs to be combined or merged in some way.  This could be a variety of things:
  - multiple "sheets" in an Excel
  - multiple files that should be combined into one data set
  - properties that need to be merged in to one data set. For example:
    - you have a table of subject properties (gender, handedness, etc.) that need to be merged into the item-level data
    - you have other information on countries (population, etc.) that need to be merged in
  - if you DON'T have this naturally-occurring issue, figure out a way to manufacture it. For example:
    - split up your data into chunks
    - make up some new table of information that you want to merge in
  - Explain (in words) what you are trying to do
  - Use binding/merging commands to accomplish this
  - Complete at least ONE example of binding and ONE example of merging


This opens the Excel Sheets
```{r}
library(readxl) 

FantasyFootball2014 <- read_excel("../Datasets/Fantasy Football 2014.xlsx", skip = 2)
FantasyFootball2015 <- read_excel("../Datasets/Fantasy Football 2015.xlsx", skip = 2)

```

Lets try to combines these two Data sets into one
```{r}
# Combining these two Data sets into one

library(dplyr)

FantasyFootball_2014x2015 <- bind_cols(FantasyFootball2014, FantasyFootball2015)
#View(FantasyFootball_2014x2015)


# Splitting Data into Two then Putting it Back Together

FantasyFootball_Left <- FantasyFootball_2014x2015[1:30]
FantasyFootball_Right <- FantasyFootball_2014x2015[31:59]

FantasyFootball_Combine <- cbind(FantasyFootball_Left, FantasyFootball_Right)
FantasyFootball_Combine
```

**Review of Merge Function**
```{r}

```


```{r}
# Split Data into Chunks then Add some New Information

        #Lets Look at Running Backs Only

        #Runningbacks 2014 Data
Runningbacks_2014 <- cbind.data.frame(FantasyFootball_2014x2015$Player[FantasyFootball_2014x2015$Pos == "RB"], FantasyFootball_2014x2015$Att[FantasyFootball_2014x2015$Pos == "RB"], FantasyFootball_2014x2015$Yds[FantasyFootball_2014x2015$Pos == "RB"], FantasyFootball_2014x2015$TD[FantasyFootball_2014x2015$Pos == "RB"], FantasyFootball_2014x2015$`1st`[FantasyFootball_2014x2015$Pos == "RB"], FantasyFootball_2014x2015$`Fan Pts`[FantasyFootball_2014x2015$Pos == "RB"],FantasyFootball_2014x2015$PPG[FantasyFootball_2014x2015$Pos == "RB"])

        #Runningbacks 2015 Data
Runningbacks_2015 <- cbind.data.frame(FantasyFootball_2014x2015$Player[FantasyFootball_2014x2015$Pos == "RB"], FantasyFootball_2014x2015$Att1[FantasyFootball_2014x2015$Pos == "RB"],  FantasyFootball_2014x2015$Yds1[FantasyFootball_2014x2015$Pos == "RB"], FantasyFootball_2014x2015$TD1[FantasyFootball_2014x2015$Pos == "RB"], FantasyFootball_2014x2015$`1st1`[FantasyFootball_2014x2015$Pos == "RB"], FantasyFootball_2014x2015$`Fan Pts1`[FantasyFootball_2014x2015$Pos == "RB"],FantasyFootball_2014x2015$PPG1[FantasyFootball_2014x2015$Pos == "RB"])


        #Merge 2014 x 2015 Data into One Dataset
Runningbacks_2014x2015 <- merge(x = Runningbacks_2014, y = Runningbacks_2015, by = "FantasyFootball_2014x2015$Player[FantasyFootball_2014x2015$Pos == ")
View(Runningbacks_2014x2015)
             
                
        #Adding Yards Per Carry Data

A1 <- FantasyFootball_2014x2015$Yds[FantasyFootball_2014x2015$Pos == "RB"]
A2 <- FantasyFootball_2014x2015$Att[FantasyFootball_2014x2015$Pos == "RB"]

Runningbacks_2014_YPC <- (A1 / A2)
Runningbacks_2014_YPC

B1 <- FantasyFootball_2014x2015$Yds1[FantasyFootball_2014x2015$Pos == "RB"]
B2 <- FantasyFootball_2014x2015$Att1[FantasyFootball_2014x2015$Pos == "RB"]

Runningbacks_2015_YPC <- (B1 / B2)


       #Merge YPC Function into One Dataset
Runningbacks_2014x2015_YPC <- cbind.data.frame(FantasyFootball_2014x2015$Player[FantasyFootball_2014x2015$Pos == "RB"], Runningbacks_2014_YPC, Runningbacks_2015_YPC)

Runningback_complete <- merge(x = Runningbacks_2014x2015, y = Runningbacks_2014x2015_YPC, by = "FantasyFootball_2014x2015$Player[FantasyFootball_2014x2015$Pos == ")
View(Runningback_complete)


```



                        
#Questions
    *How would you combine by columns if there is a differing number of rows*
          "A: Use merge function then merge columns by shared column name"