---
title: "Day 4 Lecture"
output: html_document
---

# Today's agenda

  - Review
  - PRACTICE: data type coersion
  - Lists and more on data frames
  - More on NAs, NULLs, NaNs
  - Combining data frames
  - PRACTICE: binding & merging

# Review

# Data types & coersion

```{r}
?typeof #Tells you what data type this is

typeof(FantasyFootball2014)
typeof(FantasyFootball2014$Team)


?class #Tells you "What is the thing?"

class(FantasyFootball2014)
class(FantasyFootball2014$Team)


```

`is.X` family of functions (`is.factor()`, `is.na()`, `is.finite()`, etc.)
`as.X` family of functions (`as.factor()`, `as.numeric()`, `as.data.frame()`, etc.)

# Lists
  - similar to vectors
  - can contain different data types
        *LISTS ARE HUGE BECAUSE THEY CAN CONTAIN DIFFERENT DATA TYPES*
  
  - use [[ ]] to pull out values
  - handy for glomming large/complex objects together
  
```{r}
Numeric <- c(1, 2, 3, 4, 5)
Numeric
CoercedCharacter <- c(1, "George", as.Date("2017-01-12"), factor("level1"))
CoercedCharacter
List <- list(1, "George", as.Date("2017-01-12"), factor("level1"), 1:100, head(sleep))
List
lapply(List, class)

List[6]
class(List[6]) #Says this is a list (i.e. dataframe part of the list)
class(List[[6]]) #If you want what is inside the list (dataframe is inside the list)


names(List) 
names(List) <- c("num", "name", "date", "factor", "values", "data")

List["data"] #STill gives us back a list
List[["data"]] #This gives the data part of the list specifically
List$data #This does the same as the function above
length(List)

summary(head(mysleep))
summary(List[6])
summary(List[[6]])
summary(List$data)
#  $ is the same as [[ ]]

# data.frames are (special) lists
    #Think of dataframes as a list of columns, a list is even bigger
sleep["extra"] #this brings the column
sleep$extra #this brings the data in the column
sleep[["extra"]] #this brings the data in the column

class(sleep$extra) #this is the type inside the extra column
class(sleep[["extra"]]) #this is the type inside the extra column
class(sleep["extra"]) #this is the type of sleep[extra]

length(sleep) #treats it like a list, not what we want
length(sleep$extra) #will give you length of this variable, but what if data frame has unequal n's?
nrow(sleep) #this will give you length of this dataset

identical(sleep$extra, sleep["extra"]) #is sleep$extra (the column) the same as sleep$extra (dataframe) - FALSE
identical(sleep$extra, sleep[["extra"]]) #is sleep$extra(the column) the same as sleep$extra (the column) - TRUE

```

###### NAs, NULLs

## NAs
  - missing data
  - can be a huge pain
  - no universal "handle NAs" or "ignore NAs" argument
  - sometimes `na.rm = TRUE` (like for `mean()`)
  - sometimes it's other stuff
  - `cor()` use = "pairwise.complete.obs"
  - no universal "deal with NAs" argument
          *pairwise.complete.obs () - this will ignore missing for correlations*
          *na.rm = TRUE (this will ignore missing)*
  
```{r}
x <- c(1, 2, NA, 4, 68)
mean(x)
mean(x, na.rm = TRUE)
y <- c(NA, 4, 23, 2, 6)

cor(x, y)
cor(x, y, use = "complete.obs")

x == NA
is.na(x)
!is.na(x)

```

## NULL
  - another special value
  - means "nothing" or "doesn't exist" (contrast with "missing" or "unknown")

```{r}
x <- c(1, 2, NA)
y <- c(1, 2, NULL)
x #this includes the missing value
y #this does not include the value (absence not missing)


length(x)
length(y)
x <- 1:10
y <- z <- x
y[4] <- NA
z[4] <- NULL

mysleep <- sleep
head(mysleep)
colnames(mysleep)
mysleep$ID <- NULL
head(mysleep)
colnames(mysleep)
```

## Inf, -Inf, NaN
  - can sometimes result from mathematical operations
  - helpful to be able to identify, locate them

```{r}
x <- 1/0
y <- -1/0
z <- sqrt(-4)
x
y
z

is.finite(x)
is.finite(y)
is.finite(z)
is.finite(NA)

is.infinite(x)
is.infinite(y)
is.infinite(z)
is.infinite(NA)

is.nan(x)
is.nan(y)
is.nan(z)
is.nan(NA)

is.na(x)
is.na(y)
is.na(z) # surprising to me
is.na(NA)

```

# Differences in Errors and Warnings
"R will not run if there is Error, Warning is where it will run but it may be doing it incorrectly"


---------------------------------------------------------------------------------------------------
# DATA MANIPULATION

## Combining data frame objects
### `rbind()` and `cbind()`
  - *`rbind()*`
    - glues rows on top of each other
    - expects same columns
  - *`cbind()`*
    - glues columns next to each other
    - need to be the same length
    
  - from `dplyr`
    - `bind_rows()` is better at allowing different sets/orders of columns
      - also gives you the option to "id" the the pieces you're putting together
    - `bind_cols()`
      - can also work if you give it a list argument
    
```{r}
library(dplyr)
sleep1 <- droplevels(sleep[sleep$group == "1",  ])
sleep2 <- droplevels(sleep[sleep$group == "2",  ])

summary(sleep1)
summary(sleep2)
sleep.reassembled <- rbind(sleep1, sleep2)
summary(sleep.reassembled) #no problem! data remains the same because data is identical
sleep.reassembled2 <- bind_rows(sleep1, sleep2) #will combine but now it changed the type of data
summary(sleep.reassembled2) #see now its not a factor anymore but a chracter 

"bind rows is figidity, because it wants you to make sure the factors are indentical"
"if you are putting data together that have same factor, but make sure there are same number of levels"

```

**THIS IS ACTUALLY WORTH DOING**
```{r}
sleep1$noise <- rnorm(10)

sleep.reassembled <- rbind(sleep1, sleep2)
summary(sleep.reassembled)

sleep.reassembled2 <- bind_rows(sleep1, sleep2)
summary(sleep.reassembled2)

"rbind wont let us because number of rows are different"
"bind_rows will let us and will put different number of rows as NA --->good for adding on to a dataset (i.e. maybe its taking some time to collect data, waiting on data from another condition."

```

```{r}

sleep.left <- sleep[, 1:2]
sleep.left
sleep.ID <- sleep[, 3]
sleep.ID
sleep.reassembled.2 <- cbind(sleep.left, sleep.ID)
sleep.reassembled.2

"splitting data and then putting the data back together"
```

# Merging with `merge()`

```{r}
subject.info <- data.frame(ID = 3:12, gender = c("male", "male", "female", "female", "female", "female", "male", "female", "male", "male"))
subject.info
subject.info2 <- data.frame(subject = 3:12, gender = c("male", "male", "female", "female", "female", "female", "male", "female", "male", "male"))
subject.info2

cbind(sleep, subject.info) # not what we want, it puts them together but doesn't link them.
#what we need to do is Merge
```

```{r}

sleep.merged1 <- merge(x = sleep, y = subject.info,
                       by = "ID")
          "By is what the datasets have in common (by = *name*) for fantasy dataset"

sleep.merged1


# if your columns are named different things
sleep.merged2 <- merge(x = sleep, y = subject.info2,
                       by.x = "ID", by.y = "subject")
                        "if columns are named different"
                            #by.x
                            #by.y

sleep.merged2
```

```{r}

# when you have a column that's named the same in both,
# R uses that column to merge (by default)
sleep.merged <- merge(sleep, subject.info)
?merge
sleep
sleep.merged
nrow(sleep) #All Data
nrow(sleep.merged) #NAs (after missing)


mysleep <- sleep
# when merging by a factor, BE CAREFUL, especially when
# factor levels are not the same between data.frames
mysleep$ID <- as.numeric(mysleep$ID)


sleep.merged2 <- merge(mysleep, subject.info, all = TRUE)
    "All = TRUE - shows missing values"
    "All = FAlse - does not show missing values"
sleep.merged2

```

## Getting rid of duplicate rows

```{r}
sleep.double <- rbind(sleep, sleep)
sleep.cleanedup <- unique(sleep.double)

unique(sleep$ID)
unique(c(1, 2, 2, 4, 5, 5, 6))
      #only see unique values
```

Merging notes:
    - simplest: have ONE column in common, named the same thing (with the same values)
    - can get MUCH more complex (as needed)
      - look at "join" functions in `dplyr` for alternative functions
    - `nrow()` good check on what was gained/lost during a merge
