---
title: "Day 5 Homework"
output: html_document
---

0.  Reload your data, and re-use the code you already have for getting things formatted nicely (columns renamed, factors relabeled, etc.)

```{r}
library(readxl)

FantasyFootball2014 <- read_excel("../../my_r_homework/Datasets/Fantasy Football 2014.xlsx", skip = 2)
FantasyFootball2015 <- read_excel("../../my_r_homework/Datasets/Fantasy Football 2015.xlsx", skip = 2)

head(FantasyFootball2014)
head(FantasyFootball2015)

#summary(FantasyFootball2014)
FantasyFootball2014$Pos <- as.factor(FantasyFootball2014$Pos)
FantasyFootball2014$Team <- as.factor(FantasyFootball2014$Team)

FantasyFootball2015$Pos <- as.factor(FantasyFootball2015$Pos)
FantasyFootball2015$Team <- as.factor(FantasyFootball2015$Team)
#summary(FantasyFootball2014)
#summary(FantasyFootball2015)
```

1. Aggregate (e.g., get mean/median/max/something) of some numerical variable, over one or more factors.  Use `group_by()` plus `summarize()` from the `dplyr` package. You may or may not need to reshape the data first!

```{r}
library(dplyr)

#Create Position Analysis Dataframe
#FantasyFootball2014x2015 <- merge(FantasyFootball2014, FantasyFootball2015, by = "Player")
FantasyFootball2014x2015 <- cbind(FantasyFootball2014, FantasyFootball2015)
    #View(FantasyFootball2014x2015)


Position.Analysis <- data.frame(FantasyFootball2014x2015$Player, FantasyFootball2014x2015$Pos, FantasyFootball2014x2015$DP, FantasyFootball2014x2015$`1st`, FantasyFootball2014x2015$Yds, FantasyFootball2014x2015$TD, FantasyFootball2014x2015$`1st__1`,FantasyFootball2014x2015$Yds__1, FantasyFootball2014x2015$TD__1, FantasyFootball2014$PPG, FantasyFootball2015$PPG)

names(Position.Analysis) <- c("Player", "Position", "Downs Played", "1st Downs Rushing", "Yards Rushing", "Touchdowns Rushing", "1st Downs Recieving", "Yards Recieving", "Touchdowns Recieving", "2014 PPG", "2015 PPG")
#head(Position.Analysis)

#View(Position.Analysis)

#Aggregate Data
      #Total Number of First Downs by Position (2014) (Rushing + Recieving)
      #Total Number of Yards by Position (2014) (Rushing + Recieving)
      #Total Number of Touchdowns by Position (2014) (Rushing + Recieving)

Position.Analysis$Total.First.Downs <- (Position.Analysis$`1st Downs Rushing` + Position.Analysis$`1st Downs Recieving`)
Position.Analysis$Total.Yards <- (Position.Analysis$`Yards Rushing` + Position.Analysis$`Yards Recieving`)
Position.Analysis$Total.Touchdowns <- (Position.Analysis$`Touchdowns Rushing` + Position.Analysis$`Touchdowns Recieving`)

      #Median Number of total First downs by Position (2014)
      #Median Number of Yards by Position (2014)
      #Median Number of touchdowns by Position (2014)

Median.1st <- summarize(group_by(Position.Analysis, Position), median = median(Total.First.Downs))
Median.1st

Median.Yrds <- summarize(group_by(Position.Analysis, Position), median = median(Total.Yards))
Median.Yrds

Median.Tds <- summarize(group_by(Position.Analysis, Position), median = median(Total.Touchdowns))
Median.Tds

"Very interesting. WRs on average better than RBs. I think some analysis looking at position scarcity is needed here. Perhaps the top echelon RBs are worth significantly more due to this scarcity. Recievers may be distributed more together or higher on average indicating less scarcity. Therefore, draft RBs early... Recievers you can wait."


#Alternative Method for Getting this Median Aggregate Information

A1 <- median(Position.Analysis$Total.First.Downs[Position.Analysis$Position == "RB"])
A2 <- median(Position.Analysis$Total.First.Downs[Position.Analysis$Position == "WR"])
A3 <- median(Position.Analysis$Total.First.Downs[Position.Analysis$Position == "TE"])

B1 <- median(Position.Analysis$Total.Yards[Position.Analysis$Position == "RB"])
B2 <- median(Position.Analysis$Total.Yards[Position.Analysis$Position == "WR"])
B3 <- median(Position.Analysis$Total.Yards[Position.Analysis$Position == "TE"])

C1 <- median(Position.Analysis$Total.Touchdowns[Position.Analysis$Position == "RB"])
C2 <- median(Position.Analysis$Total.Touchdowns[Position.Analysis$Position == "WR"])
C3 <- median(Position.Analysis$Total.Touchdowns[Position.Analysis$Position == "TE"])

```

2. Run TWO DIFFERENT simple analyses or statistical tests, such as linear regression (`lm()`), logistic regression (`glm()`), correlation test (`cor.test()`), t-test (`t.test()`), or non-parametric tests (e.g., `wilcox.test()`).  For each of these:
  - Describe why you are doing this analysis, i.e., what question is it answering?
  - I won't judge you on statistical expertise!  (though I will make comments if I think I can be helpful)
  - Report some key statistics from the analysis, using **inline** code. HINT: outside of an R code chunk, use `r codehere` format.
  
```{r}

#Describe the Correlations between 2014 & 2015 Fantasy Points Per Game and 1st Downs for Runningbacks. Are these correlations significant?
cor(Position.Analysis$`2014 PPG`[Position.Analysis$Position == "RB"],Position.Analysis$Total.First.Downs[Position.Analysis$Position == "RB"] )
cor.test(Position.Analysis$`2014 PPG`[Position.Analysis$Position == "RB"],Position.Analysis$Total.First.Downs[Position.Analysis$Position == "RB"] )
cor(Position.Analysis$`2015 PPG`[Position.Analysis$Position == "RB"],Position.Analysis$Total.First.Downs[Position.Analysis$Position == "RB"] )
cor.test(Position.Analysis$`2015 PPG`[Position.Analysis$Position == "RB"],Position.Analysis$Total.First.Downs[Position.Analysis$Position == "RB"] )

"Strong Positive Correlation for 2014 1st Downs for Runningbacks and 2014 Fantasy Points. Weak Correlation for 2014 1st Downs for Runningacks and 2015 Fantasy Points"


#Multiple Regression Analysis for aforementioned predictors of Fantasy Points per Game 2015
  
colnames(Position.Analysis)

Predictors.2015.FPG <- lm(`2015 PPG` ~ `2014 PPG` + `Downs Played` + `Total.First.Downs` + `Total.Yards` + `Total.Touchdowns`, data = Position.Analysis)
summary(Predictors.2015.FPG)

names(Position.Analysis) <- c("Player", "Position", "Downs.Played", "1st.Downs.Rushing", "Yards.Rushing", "Touchdowns.Rushing", "1st.Downs Recieving", "Yards.Recieving", "Touchdowns.Recieving", "PPG.2014", "PPG.2015" )


# generalTestBF(PPG.2014 ~ PPG.2015 + Downs.Played + Total.First.Down + Total.Yards + Total.Touchdowns, data = Position.Analysis)


"Very interesting. Only significant predictor for Fantasy Points for the upcoming 2015 season is Fantasy Points from 2014 Season. I assume this is the case however because of multicollinearity between the predictors. Need to transform this data in future analyses."               
```

3. Get your data into "long" (aka "tidy") format, if it isn't already

```{r}
library(tidyverse)

Position.Analysis.long <- gather(Position.Analysis, Variables, Position, `Downs Played`:`Median.TDs`)
View(Position.Analysis.long)
```


